To Do List

### 2018-10-03 ToDo.Rmd
completed tasks

>>>>

+ add standardization part to question 4 table
+ question 6: which variable selection technique?
+ perform scaling with transformation

## 10/01/18

* read up on random forest 
   - investigate how to get final decision tree
   - how variable importance is calculated
+ write about answers not questions; make headers as answers not questions
+ investigate how many iterations are necessary for under sampling
   - plot it
* investigate svm & neural networks & naiive bayes
